---
title: "Movie_Rating"
author: "Ashish Pal"
date: "October 7, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library('caret') 

```

# Frame
## Data Visualization (EDA) for Movie Rating based on given Factors.

# Acquire
```{r}
setwd("C:/Users/Ashish/Desktop/GL/Day2/HomeWork/Movie_Rating Assg")

Movie_data = read.csv("Movie-ratings.csv", stringsAsFactors = FALSE)

Movie_data1 = Movie_data
```
# Refine & Transform
```{r}
str(Movie_data1)

#Check for missing value or NA value
colSums(is.na(Movie_data1))
colSums(Movie_data1 == '')
colSums(Movie_data1 == 0)

#This clearly shows there is no NA or missing value in our dataset
# But there are 8 Movies who's Budget is Zero which is practically impossible. 
# Let's replace it with mean of Budget. 


s = mean(Movie_data1$Budget..million...)
Movie_data1$Budget..million...[Movie_data1$Budget..million... == 0] = s


apply(Movie_data1,2, function(x) length(unique(x)))
##We can also see that Genre & Year.of.release is a Factor.Let's convert it into Factor

Movie_data1$Genre = as.factor(Movie_data1$Genre)
Movie_data1$Year.of.release = as.factor(Movie_data1$Year.of.release)

col_name = c ("Film","Genre","Critics.Ratings","Audience.Ratings","Budget.Million","Year")
colnames(Movie_data1) = col_name
str(Movie_data1)

# Number of movies in each year in our dataset. 
#2007
Movie_data1 %>% filter(Year == 2007) %>% count()
#2008
Movie_data1 %>% filter(Year == 2008) %>% count()
#2009
Movie_data1 %>% filter(Year == 2009) %>% count()
#2010
Movie_data1 %>% filter(Year == 2010) %>% count()
#2011
Movie_data1 %>% filter(Year == 2011) %>% count()

# Let's gather Ratings into one variable - 
Movie_data2 = Movie_data1 %>% gather("Rating.Source","Rating",3:4) %>% arrange(Year)
str(Movie_data2)


```
#Explore

## 1. Movies Data analysis and checking outliers -

```{r}
ggplot(Movie_data1) + aes(Year)+geom_bar()

ggplot(Movie_data2)+aes(Rating.Source,Rating) +geom_boxplot()+ facet_grid(~Year)
```

##Infer 1-
### This shows Year 2007 is having comparatively less movies than oher years in  our Dataset. 
### Another Important Observation is Audience Rating average is greater than Critics Rating. Also Critics Rating is spread over wide range compare to Audience Rating.




## 2 . Exploratory Analysis on Genre & Year 

```{r}

ggplot(Movie_data1, aes(x = Year, fill = Genre)) + geom_bar(position = "dodge") + scale_x_discrete("Year") + scale_y_continuous("Number of Movies")

ggplot(Movie_data1, aes(x = Genre, fill = Year)) + geom_bar(position = "dodge") + scale_x_discrete("Genre") + scale_y_continuous("Number of Movies") 

```

## Infer 2 -
###The above 2 Graphs shows that maximum Movies produced between year 2007 to 2011 are Comedy and Action followed by Drama and then Horror. 
### The Thriller and Romance movies number has increased in the year 2011. 

## 3. Exploratory Analysis on Genre & Critics.Ratings / Audience.Ratings
```{r}
ggplot(Movie_data1)+aes(x = Critics.Ratings,fill = Genre)+geom_histogram() + facet_grid(~Year)+
xlab("Critics.Ratings") +  ylab("Frequency") + ggtitle("Critics.Ratings for Each Genre & Year")
#+scale_x_continuous(breaks=seq(20,75,10)) + 
 # scale_y_continuous(breaks=seq(0,1700,250))  
                
ggplot(Movie_data1)+aes(x = Audience.Ratings,fill = Genre)+geom_histogram() + facet_grid(~Year)+
xlab("Audience.Ratings") +  ylab("Frequency") + ggtitle("Audience.Ratings for Each Genre & Year")  
```

##Infer 3 - 
### The Above 2 graphs clearly shows that Overall Movie ratings(Audience & Critic) has increased from Year 2007 to 2011. 

## 4 .Exploratory Analysis on Genre & Budget & Year 
```{r}
ggplot(Movie_data1)+aes(x = Budget.Million,fill = Genre)+geom_histogram(binwidth = 30) + facet_grid(~Year)+
xlab("Budget") +  ylab("Frequency") + ggtitle("Budget for Each Genre & Year")  
              
```

## Infer 4 - 
### Majority of Movies are having Budget below $100 Million 
### High Budget movies are generally Action Movies

## 5. Exploratory Analysis on Genre & Critics.Ratings vs Audience Ratings
## CEO's Vision

```{r}
# Let's Analyse data statistically - 
## How much Crtitics Ratings differ from Audience Ratings - 

mean(Movie_data1$Critics.Ratings)
mean(Movie_data1$Audience.Ratings)

# As we can see overall Audience Rating's mean is greater than Crtics Rating's mean- 
cov(Movie_data1$Critics.Ratings,Movie_data1$Audience.Ratings)

# It shows a strong Positive relation between two ratings 
cor(Movie_data1$Critics.Ratings,Movie_data1$Audience.Ratings)

##########################################################################
Movie_data1  %>% 
  ggplot() +aes(x = Audience.Ratings, y = Critics.Ratings) + geom_point() + geom_smooth(method = "lm") +facet_grid(~Year)

ggplot(Movie_data1)+aes(x = Critics.Ratings,y = Audience.Ratings, col = Genre)+geom_point() + facet_grid(~Year)

ggplot(Movie_data1)+aes(x = Critics.Ratings,y = Audience.Ratings, col = Genre)+geom_point() + facet_grid(~Year) +
geom_smooth(method = "lm",se =FALSE) +
geom_smooth(aes(group = 1), method = "lm", se = FALSE, linetype = 2)  

ggplot(Movie_data1)+aes(x = Critics.Ratings,y = Audience.Ratings, col = Genre)+geom_point() + facet_grid(~Year)

```


##Infer 5 - 
### 1.This clearly shows thier is direct Positive relationship(Correlation) between Audience rating and critings Rating.
### 2.The graph also reflects that with increasing year the Correlation between both ratings has increased. 
### 3.There is no clear view for Genre and Ratings
### 4. The Year 2011 rating is more linear than previous ratings which reflect Audience & Critics Ratings are become more similar. 

## 6. Exploratory Analysis on Genre & Critics.Ratings vs Audience Ratings
```{r}

# Let's make Budget into a category Small, Medium and Big Budget. 
Movie_data3 = Movie_data1
range(Movie_data3$Budget.Million)


Movie_data3$Budget.Million = cut(Movie_data3$Budget.Million , breaks =  c(0,100,200,301),labels = c("Small","Medium","Big"))

str(Movie_data3)

ggplot(Movie_data3)+aes(x = Critics.Ratings,y = Audience.Ratings, col = Budget.Million )+geom_point() + facet_grid(~Year)+
xlab("Critics Rating") +  ylab("Audience Ratings") + ggtitle("Variation of Ratings on other facctors")  
              
ggplot(Movie_data3)+aes(x = Critics.Ratings,y = Audience.Ratings, size = Budget.Million , col = Genre)+geom_point() + facet_grid(~Year)+
xlab("Critics Rating") +  ylab("Audience Ratings") + ggtitle("Variation of Ratings on other facctors")  

 

```

## Infer 6 
### Apart from Infer4 this shows Budget of the Movie do not influence Crtics Rating much but have impact on Audience rating. 


