---
title: "LabWork"
author: "Ashish Pal"
date: "September 22, 2017"
output:
  html_document: default
  pdf_document: default
---
## Analysis Onion Data for the year 2017 and predicting for future Year

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Reading libraries
library(rvest)
library(tidyr)
library(dplyr)
library(stringr)
library(ggplot2)
library(prophet)
```

# Frame
1st part - Find the State with the highest quantity sales.
2nd part - Predict the daily price for the next 30 days for that state.

#Acquire
Getting data from NHRDF Database

```{r}
setwd("C:/Users/Ashish/Desktop/GL/Day2/HomeWork")
getwd()
Odf = read_html("DailyWiseMarketArrivals2017.html") %>%
html_node("#dnn_ctr966_DailyWiseMarketArrivals_GridView1") %>%
html_table()
Odf_1 = Odf
str(Odf_1)
```

# Refine 
```{r}
col_names =  c("Date","Market","Quantity","Min_Price","Max_Price","Mod_Price")
colnames(Odf_1) = col_names
str(Odf_1)
```

#Transfrom
```{r}
Odf_2 = Odf_1
Odf_2$Date = as.Date(Odf_1$Date, "%d/%b/%Y")
Odf_2$Min_Price = as.numeric(Odf_2$Min_Price)
Odf_2$Max_Price = as.numeric(Odf_2$Max_Price)
Odf_2$Mod_Price = as.numeric(Odf_1$Mod_Price)
str(Odf_2)
```

```{r}
dim(Odf_2)
Odf_3 = Odf_2 %>% filter(Market != "Total") %>% mutate(market1 = Market) %>%  separate(market1,c("city","state"), sep = "\\(")
dim(Odf_3)
Odf_3$state = Odf_3$state %>% str_replace("\\)","")
head(Odf_3)
unique(Odf_3$state)

```

```{r}
# Removing NA fields from state
Odf_4 <- Odf_3 %>% mutate(state = ifelse(is.na(state), Market, state))

Odf_4 = within(Odf_4,state[state == "Telangana"] <- "TELANGANA")
Odf_4 = within(Odf_4,state[state == "RJ" ]<- "RAJ")
Odf_4 = within(Odf_4,state[state == "M.P."] <- "MP")
Odf_4 = within(Odf_4,state[state == "JAIPUR"] <- "RAJ")
Odf_4 = within(Odf_4,state[state == "MS"] <- "MAHARASHTRA")
Odf_4 = within(Odf_4,state[state == "BANGALORE"] <- "KNT")
Odf_4 = within(Odf_4,state[state == "MS"] <- "MAHARASHTRA")
Odf_4 = within(Odf_4,state[state == "BHOPAL"] <- "MP")
Odf_4 = within(Odf_4,state[state == "CHENNAI"] <- "TN")
Odf_4 = within(Odf_4,state[state == "TN "] <- "TN")
Odf_4 = within(Odf_4,state[state == "HYDERABAD"] <- "AP")
Odf_4 = within(Odf_4,state[state == "LUCKNOW"] <- "UP")
Odf_4 = within(Odf_4,state[state == "SHAHJAHANPUR"] <- "UP")
unique(Odf_4$state)

```

#Explore 
## State with Highest Quantity Sales in 2017
```{r}

sum_quantity_df <- Odf_4 %>% 
group_by(state) %>% 
summarize(sum_quantity = sum(Quantity),avg_price = mean(Max_Price))
str(sum_quantity_df)
Top_quantity = sum_quantity_df %>%
  arrange(desc(sum_quantity))

head(Top_quantity)

#Visualizing data
Top_quantity %>% head(10) %>% ggplot() + aes(state, weight = sum_quantity) + geom_bar()

Top_quantity %>% head(10) %>% ggplot() + aes(state, weight = sum_quantity) + geom_bar()+coord_flip()

Top_quantity %>% head(10) %>% ggplot() + aes(reorder(state,sum_quantity), weight = sum_quantity) + geom_bar()+coord_flip()

str(Odf_4)

p3 <- ggplot(Odf_4,
             aes(x = state,
                 y = Mod_Price)) + 
        theme(legend.position="top",
              axis.text=element_text(size = 6))
(p4 <- p3 + geom_point(aes(color = Date),
                       alpha = 0.5,
                       size = 1.5,
                       position = position_jitter(width = 0.25, height = 0)))


```
# This clearly shows that MAHARASHTRA is the state with highest quantity sale. 

# Predicting price of Onion for state = MAHARASHTRA for next 30 days. 

```{r}
Ms_Price = Odf_4 %>% filter(state == "MAHARASHTRA") %>% group_by(Date) %>% summarise(Mod_Price_max = max(Mod_Price)) %>% select(Date,Mod_Price_max) %>% arrange(Date)


dim(Ms_Price)
head(Ms_Price)
str(Ms_Price)

col1 = c("ds","y")
colnames(Ms_Price) = col1
d =Ms_Price
m = prophet(d)

future <- make_future_dataframe(m, periods = 365)
head(future)

forecast <- predict(m, future)
head(forecast)

plot(m, forecast)
prophet_plot_components(m, forecast)
 
```



