---
title: "Titanic"
author: "Ashish Pal"
date: "October 5, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Titanic dataset from Kaggle

#Frame - 
1. Analysis of factors/Variables which will affect Survival rate.
3. Prediction  of Survival for test data

# Acquire 
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library('caret') 
library('randomForest') 
library('rpart')
library('rpart.plot')
library('car')
library('e1071')
setwd("C:/Users/Ashish/Desktop/DataSets/Titanic")
train_t = read.csv("train.csv" ,stringsAsFactors = F)
test_t = read.csv("test.csv",stringsAsFactors = F)
str(train_t)
head(test_t)

```

# Refine & Transform 
```{r}
# Let's analyse Data and different variables
# clearly Survived is a output (dependent variable) and others are independent variable.

# let's find out missing or NA values - 

colSums(is.na(train_t))
 
colSums(train_t == '')
### Let's convert Empty embarked variable with max occuring one - 
table(train_t$Embarked)
train_t$Embarked[train_t$Embarked == ""]="S"
table(train_t$Embarked)
### Let's check number of values in each variable to distinguish them - 

apply(train_t,2, function(x) length(unique(x)))
### This clearly shows Survived , Pclass , Sex, Embarked are factor variable. 

cols=c("Survived","Pclass","Sex","Embarked")
for (i in cols){
  train_t[,i]=as.factor(train_t[,i])
}

str(train_t)
```

## Feature Engineering/Transform 

```{r}
### As we can see we can extract information from name variable. 
train_t$title = gsub('(.*, )|(\\..*)', '', train_t$Name)
table(train_t$title)

# Titles with very low cell counts to be combined to "rare" level
rare_title <- c('Dona', 'Lady', 'the Countess','Capt', 'Col', 'Don', 
                'Dr', 'Major', 'Rev', 'Sir', 'Jonkheer')

# Also reassign mlle, ms, and mme accordingly
train_t$title[train_t$title == 'Mlle']        <- 'Miss' 
train_t$title[train_t$title == 'Ms']          <- 'Miss'
train_t$title[train_t$title == 'Mme']         <- 'Mrs' 
train_t$title[train_t$title %in% rare_title]  <- 'Rare Title'

# Show title counts by sex again
table(train_t$Sex, train_t$title)

str(train_t)
```
## Explore 
### We can see Pclass , Sex , Age , sibsp & Parch , Title and Embarked could be major Factors which can help in analsing survived variable and trend. 

##Exploratory Analysis on Pclass & Sexx
```{r}
# Lets visualize the relationship between Sex & survival
ggplot(train_t) + aes(Sex,fill = factor(Survived))+geom_bar()+
ggtitle("Sex v/s Survival Rate")+
xlab("Sex") +
ylab("Total Count") +
labs(fill = "Survived") 

# This clearly shows that Probablilty/chance of Survival for female is much more for than male. 


# Lets visualize the relationship between Pclass & survival
ggplot(train_t) + aes(Pclass,fill = factor(Survived))+geom_bar()+
ggtitle("Pclass v/s Survival Rate")+
xlab("Pclass") +
ylab("Total Count") +
labs(fill = "Survived")

## First class Survival rate is far more better than the 3rd class  
## No doubt Rich peope having better Survival rate than the poor

# Let's Visualize the 3-way relationship of sex, pclass, and survival
ggplot(train_t, aes(x = Sex, fill = Survived)) +
geom_bar() +
facet_wrap(~Pclass) + 
ggtitle("3D view of sex, pclass, and survival") +
xlab("Sex") +
ylab("Total Count") +
labs(fill = "Survived")

##In all the class female Survival rate is better than Men

```
##Exploratory Analysis on Title

```{r}
ggplot(train_t,aes(x = title,fill=factor(Survived))) +
  geom_bar() +
  ggtitle("Title V/S Survival rate")+
  xlab("Title") +
  ylab("Total Count") +
  labs(fill = "Survived") 

##In the titanic you are Mr then there is less chance of survival, Miss and Mrs having better survival rate then Master and Officer 

### Visualize the 3-way of relationship of Title, Pclass, and Survival

ggplot(train_t, aes(x = title, fill = Survived)) +
  geom_bar() +
  facet_wrap(~Pclass) + 
  ggtitle("3-way relationship of Title, Pclass, and Survival") +
  xlab("Title") +
  ylab("Total Count") +
  labs(fill = "Survived")

##Master in 1st and 2nd class has 100% Survival where has Mrs and Miss having 90% chance of Survival in 1st and 2nd class 
##Since Title mostly depending on Age (except few cases), I will use title in place of age which has 263 missing observation

```
## Exploratory Analysis on Family

```{r}
# Lets create a Family size using Sibsp and Parch


train_t$FamilySize <-train_t$SibSp + train_t$Parch + 1

train_t$FamilySized[train_t$FamilySize == 1]   <- 'Single'
train_t$FamilySized[train_t$FamilySize < 5 & train_t$FamilySize >= 2]   <- 'Small'
train_t$FamilySized[train_t$FamilySize >= 5]   <- 'Big'

train_t$FamilySized=as.factor(train_t$FamilySized)


###Lets Visualize the Survival rate by Family size 
ggplot(train_t,aes(x = FamilySized,fill=factor(Survived))) +
  geom_bar() +
  ggtitle("Family Size V/S Survival Rate") +
  xlab("FamilySize") +
  ylab("Total Count") +
  labs(fill = "Survived")


###Big Family in Titanic having worst survival rate then Smaller and Alone

####Why Big Family has a probelm?, Check in the below visualization

ggplot(train_t, aes(x = FamilySized, fill = Survived)) +
  geom_bar() +
  facet_wrap(~title) + 
  ggtitle("3D View of Fmily Size, Title and Survival rate") +
  xlab("family.size") +
  ylab("Total Count") +
  ylim(0,300) +
  labs(fill = "Survived")



##You are a Master in the Big Family your Survival rate is absolutely nill even though overall survival rate of master is very good


ggplot(train_t, aes(x = FamilySized, fill = Survived)) +
  geom_bar() +
  facet_wrap(~Pclass) + 
  ggtitle("3D View of Fmily Size, Title and Survival rate") +
  xlab("family.size") +
  ylab("Total Count") +
  ylim(0,300) +
  labs(fill = "Survived")

### Now this clearly shows that max big families are from class 3 and hence survival rate is least.

```
##Exploratory Analysis on Embarked
```{r}

###is there any association between Survial rate and where he get into the Ship.   
 ggplot(train_t,aes(x = Embarked,fill=factor(Survived))) +
  geom_bar() +
  ggtitle("Embarked vs Survival") +
  xlab("Embarked") +
  ylab("Total Count") +
  labs(fill = "Survived") 

# There is no correlation between survival rate and embarked.

```

#Model 


```{r}
str(train_t)
feauter1<-train_t
response <- as.factor(train_t$Survived) 
feauter1$Survived=as.factor(train_t$Survived)

###For Cross validation purpose will keep 20% of data aside from my orginal train set
##This is just to check how well my data works for unseen data
set.seed(500)
ind=createDataPartition(feauter1$Survived,times=1,p=0.8,list=FALSE)
train_val=feauter1[ind,]
test_val=feauter1[-ind,]

str(train_val)

#Lets run Logistic regression model
log.mod <- glm(Survived ~ Pclass+Sex+title+FamilySize, family = binomial(link=logit), 
               data = train_val)
###Check the summary
summary(log.mod)

confint(log.mod)

###Predict train data
train.probs <- predict(log.mod, data=train_val,type =  "response")
table(train_val$Survived,train.probs>0.5)

(397+196)/(397+196+78+43)

###Logistic regression predicted train data with accuracy rate of 0.83 


test.probs <- predict(log.mod, newdata=test_val,type =  "response")
table(test_val$Survived,test.probs>0.5)

(96+53)/(96+53+13+15)

###Logistic regression predicted test data with accuracy rate of 0.84


```
# Infer

## We can clearly see Title/ Sex , Family Size and Pclass are major Factors in Predicting Survival rate of each Passenger. 

```{r}
# Let's visualize
ggplot(train_t, aes(x = FamilySized, fill = Survived)) +
  geom_bar() +
  facet_wrap( title ~ Pclass) + 
  ggtitle("3D View of Fmily Size, Title and Survival rate") +
  xlab("family.size") +
  ylab("Total Count") +
  ylim(0,300) +
  labs(fill = "Survived")

```

##  -> Also we can Infer that Pclass 3 Adult Male having least Survival rate. 
##  -> Pclass 1 Female childerns are having Highest Probabalilty of Survival. 
##  -> Among Families Small families and Single People survival rate is much better than Big Families. 